---
title:
author: "afilazzola and cjlortie"
date: "Dec 2016"

    
---
    
Meta-data
In a greenhouse on November 20th 2014, five Ephedra seeds were placed in 160 four inch pots mixed with different ratios of potting soil and sand. On January 9th 2015 all the emerged plants were removed leaving behind only one plant that was surveyed for height and survival until February 25th, 2015. 

Micro:	Place open in full sun or under a shade structure.
Sand:	Percentage of soil composition that is sand
Rep:	Replicate
Cenus:	survey event
Date:	day that the survey was begun
Emergence:	number of plants that emerged from the seeds. 
Survival:	number of plants that have survived
Height: length of plant found in each pot (cm).

---
```{r data & library input}
library(tidyverse)
substrate <-read.csv("data/ephedra.substrate.csv")
recruit <-read.csv("data/ephedra.recruitment.csv")
landscape <-read.csv("data/ephedra.landscape.csv")

## functions
## inverse hyperbolic sine transformation 
ihs <- function(x) {
    y <- log(x + sqrt(x ^ 2 + 1))
    return(y)
}

```


### Ephedra recruitment at landscape
```{r}

plot(landscape$RDM.2013, landscape$Shrub.density)

m1 <- lm(ihs(RDM.2013)~ Shrub.density* Volume,data= landscape)
